\LARGE \bf \pyRobots, a toolkit for robot executive control

### 2014-09-03 paper.tex
Section on logging/debugging

\end{pythoncode*}
\caption{Examples of poses normalizing.}
\label{lst:poses}
\end{listing}

@@

\section{Detailed Example}

>>>>

\end{pythoncode*}
\caption{Examples of pose normalization.}
\label{lst:poses}
\end{listing}

@@

Running robots in real-world, \ie dynamic and unpredictable, environments
entails repetitive coding-testing-debugging development cycles. \pyRobots
provides several tools to support this development phase. A special attention
was paid to the logging infrastructure. It relies on the versatile Python
built-in logging tools, which support configurable parallel logging streams
(typically, a full debug stream is logged to a file while a less verbose stream
is output on the console at run-time).

\pyRobots logs are designed to allow full \emph{post-mortem} replay, and we
provide a graphical interface to display the actions and resource usage over
time (Figure~\ref{log_view}).

Debugging and introspection support is provided at run-time through a range of
off-the-shell Python debuggers. Remote debugging is also supported with standard
tools like {\sc rpdb2}~\footnote{\url{http://winpdb.org}}. Thanks to the dynamic
nature of Python, these debuggers not only provide insights on failures, but
also provide full introspection and run-time manipulation of the application
state.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Detailed Example}
